>

### 2019-11-13 manuscript/manuscript.Rmd
Edits for grammar.

In spite of the flexibility of adapted isochrone techniques, the arbritrary
definitions necessarily imposed by researchers in its application can inhibit
holistic analysis [@Logan2017].
A somewhat more complete approach is the so-called "gravity" accessibility
statistic. In this case the accessibility of point $i$ is the denominator of the
gravity formulation of a trip distribution model,
\begin{equation}\label{eq:gravity}
A_i = \sum_{j = 1}^J S_j f(d_{ij})
\end{equation}
where $S_j$ is the "size" of each park literally (i.e. acres) or abstractly (i.e.
trip attractions) and $f(d_{ij})$ is a monotonically decreasing cost function,
usually a negative exponential. @Dong2006 note that the isochrone framework is a
special case of the gravity model where $f(d_{ij})$ is a binary function and
$S_j = 1$.
@Giles-Corti2005 compare various gravity-based accessibility scores with an
isochrone specification and show that the former are more predictive of walking
behavior; that is, the attributes of a park matter influence walking more than
merely the distance to it. @Zhang2011 develop a population-weighted,
gravity-based accessibility to parks metric with a national scope, though they
do not examine its correlation with health outcomes.

@@

We calculate a set of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
the park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in the Alameda County (Oakland), California by applying
this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. We do not have
access to the necessary data to repeat the @Macfarlane2019 methodology in New
York is cost-prohibitive, and the public parks datasets in Alameda County are
not sufficiently detailed to perform the present accessibility analysis there.
In the absence of park trip destination choice coefficients in New York City, we
adopt these previous estimates.

@@

Table \ref{tab:pa-models} present the estimated spatial lag and accessibility
coefficients for three models using different specifications of the utility
equation, as well as the ten-minute walk buffer calculated by ParkScore. 
Note that the model called "Size and Distance" is precisely the model
labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
suppressed for clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in the Appendix. Each of the three
utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
and is of the hypothesized directionality. That is, residents living in tracts 
with increased utility-based accessiblity to green spaces show a significantly
higher physical activity participation rate. Taking the rough mean of the three
estimated utility-based coefficient, moving from the least-accessible tract ($A_i = -3$) to the
most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
by `r 6 * .2` percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor park access
is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.

>>>>

In spite of the flexibility of adapted isochrone techniques, the arbritrary
definitions necessarily imposed by researchers in its application can inhibit
holistic analysis [@Logan2017].
A somewhat more complete approach is the so-called "gravity" accessibility
statistic. In this case the accessibility of point $i$ is the denominator of the
gravity formulation of a trip distribution model,
\begin{equation}\label{eq:gravity}
A_i = \sum_{j = 1}^J S_j f(d_{ij})
\end{equation}
where $S_j$ is the "size" of each park literally (i.e. acres) or abstractly (i.e.
trip attractions) and $f(d_{ij})$ is a monotonically decreasing cost function,
usually a negative exponential. @Dong2006 note that the isochrone framework is a
special case of the gravity model where $f(d_{ij})$ is a binary function and
$S_j = 1$.
@Giles-Corti2005 compare various gravity-based accessibility scores with an
isochrone specification and show that the former are more predictive of walking
behavior; that is, the attributes of a park influence walking more than
merely the distance to it. @Zhang2011 develop a population-weighted,
gravity-based accessibility to parks metric with a national scope, though they
do not examine its correlation with health outcomes.

@@

We calculate a set of utility-based accessibility statistics for each tract
in New York City. The most basic utility specification includes only the
park size in acres and the distance from the population-weighted tract centroid
to the boundary of the park in miles,
\begin{equation}\label{eq:u_access}
V_{ij} = \lambda_s * \log(size_j) + \lambda_d * \log(distance_{ij})
\end{equation}
The logarithmic transform allows for diminishing marginal utility of distance
and park size: A 1-mile increase to a trip matters more for a 1-mile trip than a
10-mile trip. @Macfarlane2019 estimated destination choice 
parameters for park trips in Alameda County (Oakland), California by applying
this utility specification to passively collected mobile device data, obtaining values of $\lambda_s = 0.373$ and 
$\lambda_d = -1.76$. The ratio of these estimates implies people are willing to
travel roughly six times further to reach a park twice as large. We do not have
access to the necessary data to repeat the @Macfarlane2019 methodology in New
York, and the public parks datasets in Alameda County are
not sufficiently detailed to perform the present accessibility analysis there.
In the absence of park trip destination choice coefficients in New York City, we
adopt these previous estimates.

@@

Table \ref{tab:pa-models} presents the estimated spatial lag and accessibility
coefficients for three models using different specifications of the utility
equation, as well as the ten-minute walk buffer calculated by ParkScore. 
Note that the model called "Size and Distance" is precisely the model
labeled "SDEM" in Table \ref{tab:slx-sdem}. The controlling covariates are
suppressed for clarity but do not change meaningfully across the four specifications.
Complete model estimates are available in the Appendix. Each of the three
utility-based specifications is significant at the $\alpha = 0.05$ level or lower,
and is of the hypothesized directionality. That is, residents living in tracts 
with increased utility-based accessiblity to green spaces show a significantly
higher physical activity participation rate. Taking the rough mean of the three
estimated utility-based coefficients, moving from the least-accessible tract
($A_i = -3$) to the
most-accessible tract ($A_i = 3$) is expected to raise the physical activity rate
by `r 6 * .2` percentage points. With the understanding of the full 95\% confidence
interval, we could suggest that the true effect of excellent versus poor park access
is anywhere between `r 6 * .05` and `r 6 * .35` percentage points.
